---
title: "R Plotting Functions for Model Development"
output: html_notebook
---


```{r}
# source file with plotting functions
source('~/Desktop/R Code/shiny_plotter/plotter_functions.R')
```


```{r}

# read sample data sets for plotting
census <- read.csv("~/Desktop/us_census_income/census_train.csv")
white <- read.csv('~/Desktop/wine_quality/winequality-white.csv', sep=";")
```



c_plot_numeric(df$age, df$income50k, bins=30)


c_plot_factor(df$marital.status, df$income50k)
c_plot_factor(df$major.occupation.code, df$income50k, show_max = 5)
c_plot_factor(df$state.of.previous.residenc, df$income50k, show_max=10)




white <- read.csv('~/Desktop/wine_quality/winequality-white.csv', sep=";")
head(white)



n_plot_numeric(white$residual.sugar, 
               white$volatile.acidity, 
               samp_size=500,
               line=TRUE,
               x_log=TRUE, 
               y_log=FALSE,
               xname="Sugar", 
               yname="Acidity")
               

n_plot_factor(df$marital.status, df$age, xname="Marital Status", yname="Age", 
              y_log=FALSE, show_max=5)

n_plot_factor(df$major.occupation.code, df$age, xname="Marital Status", yname="Job", 
              y_log=FALSE)
               
               
